SunPy - Python for Solar Physics

### 2014-08-28 reply_referee.txt

1) We agree that the paper should illustrate how SunPy enables science. To that end, we have added descriptions in the Introduction section of typical workflows for solar physicists and discuss how the features of SunPy are suited to enabling those workflows.

2)

3)

4) In the example on p.11, the term ‘coronagraphs’ was included here by mistake. Instead, the query result ‘lasco_query’ should have been referred to. The listing has been corrected.

@@

3) The referee is correct - the CompositeMap and MapCube descriptions were accidentally reversed. CompositeMap should refer to spatially aligned data and MapCube to temporally aligned data. We have corrected the text of the manuscript in Section 2.1.

4) We decided to remove the term 'factory' from the description of Map, as in the end we do not discuss this any further throughout the manuscript, and may cause confusion. We instead refer more generally to the Map creation.

5) We add to our discussion of units in SunPy, as the referee suggested. The goal of SunPy in the future is for all units to be handled using the Astropy sub-package. As of 0.5 however this feature has not been implemented, except in the sunpy.sun module. This is now discussed in Section 4 of the manuscript.

6) We agree with the referee that more Python-like idioms should be used in the code listing examples. Code snippets such as lasco_query.num_records() (e.g. Listing 6) have hence been replaced with len(lasco_query.records) throughout the manuscript.

7) We have clarified the construction of the file paths in Listing 6 by adding more description to the Listing caption. We have also endeavored to clarify the code listings throughout the manuscript, as the referee has suggested.

@@

8)

9) We agree with the referee that full descriptions of the allowed attrs should be easily available for HEK and VSO. Unfortunately this feature is not yet available within SunPy. However, we plan to address this in the near future.

### 2014-08-28 2-1-Map.tex
cleaned up map instrument list

\begin{itemize}
\item \textit{Yohkoh}/SXT - SXT: Solar X-ray Telescope \citep{1991SoPh..136....1O, 1991SoPh..136...37T},
\item \textit{SOHO}/EIT and LASCO - SOHO: Solar and Heliospheric Observatory \citep{domingo1995}, EIT: Extreme Ultraviolet Telescope \citep{1995SoPh..162..291D} and LASCO: Large Angle Spectroscopic COronagraph \citep{1995SoPh..162..357B}
\item \textit{RHESSI} - RHESSI: Reuven Ramaty High Energy Solar Spectroscopic Image \citep{2002SoPh..210....3L},
\item \textit{STEREO}/EUVI and COR1/2 - STEREO: Solar TErrestrial RElations Observatory \citep{2005AdSpR..36.1483K}, EUVI: Extreme Ultraviolet Imager \citep{2004SPIE.5171..111W} and COR1/2: CORonagraph 1/2 \citep{2002AdSpR..29.2017H}
\item \textit{Hinode}/XRT - XRT: X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.
\item \textit{PROBA2}/SWAP - PROBA2: PRojects for On Board Autonomy 2 \citep{2013SoPh..286....5S}, SWAP: Sun Watcher Active Pixel \citep{2013SoPh..286...43S}
\item \textit{SDO}/AIA and HMI - HMI: Helioseismic Magnetic Imager, \citep{2012SoPh..275..207S}
\item \textit{IRIS} - IRIS: Interface Region Imaging Spectrograph \citep{2011SPD....42.1512L} SJI (slit-jaw imager) frames.           
\end{itemize}

>>>>

\begin{itemize}
\item \textit{Yohkoh} Solar X-ray Telescope (SXT; \citealp{1991SoPh..136....1O, 1991SoPh..136...37T}),
\item Solar and Heliospheric Observatory (\textit{SOHO}; \citealp{domingo1995}) Extreme Ultraviolet Telescope (EIT; \citealp{1995SoPh..162..291D})
\item \textit{SOHO} Large Angle Spectroscopic COronagraph (LASCO; \citealp{1995SoPh..162..357B})
\item \textit{RHESSI} - Reuven Ramaty High Energy Solar Spectroscopic Imager \citep{2002SoPh..210....3L},
\item Solar TErrestrial RElations Observatory (\textit{STEREO}; \citealp{2005AdSpR..36.1483K}) Extreme Ultraviolet Imager (EUVI; \citep{2004SPIE.5171..111W})
\item \textit{STEREO} CORonagraph 1/2 (COR 1/2; \citealp{2002AdSpR..29.2017H})
\item \textit{Hinode} XRT - X-Ray Telescope \citep{2007SoPh..243....3K, 2007SoPh..243...63G}.
\item PRojects for On Board Autonomy 2 (\textit{PROBA2}; \citealp{2013SoPh..286....5S}) Sun Watcher Active Pixel (SWAP; \citealp{2013SoPh..286...43S})
\item \textit{SDO} AIA and HMI: Helioseismic Magnetic Imager, \citep{2012SoPh..275..207S}
\item Interface Region Imaging Spectrograph (\textit{IRIS}; \citealp{2011SPD....42.1512L}) SJI (slit-jaw imager) frames.           
\end{itemize}
